Morus: Biases in the stream

### 2018-05-07 morusAC.tex
Added differential trail

\subsubsection{Differential Trails.}

>>>>

\subsubsection{Differential Trails.}
Recall that the message input during the finalization of \cipher{MORUS1280} is $adlen\|msglen\|0^{128}$ where $adlen$ and $msglen$ are 64-bit strings. We set $\Delta adlen$ to be low Hamming weight, namely {\tt 0x0000000000000001}. Hereafter, we use {\tt typefont} denote hexadecimal numbers. This difference propagates during the subsequent 3 steps as specified in Table~\ref{Tbl:fin_diff}.

\begin{table}[!tb]
\begin{center}
\caption{Differential Propagation through 3 Steps in the Finalization.}
\label{Tbl:fin_diff}
{\tiny
\begin{tabular}{cccccc}
Round & \multicolumn{4}{c}{State Difference} & Weight \\ \hline
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
PT    & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\ \hline

      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
1     & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\ \hline

      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000400000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 1 \\
2     & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\ \hline

      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000400000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 1 \\
3     & {\tt 0000004000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 1 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\ \hline

%Weight: 0
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000400000000000} & {\tt 0000000000000000} & 1 \\
4     & {\tt 0000004000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 1 \\
      & {\tt 0020000000000080} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\ \hline

%Weight: 1
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 0 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000400000000000} & {\tt 0000000000000000} & 1 \\
5     & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000004000000000} & 1 \\
      & {\tt 0020000000000080} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0000040000000010} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\ \hline

%Weight: 3
      & {\tt 0000000000100004} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000400000000000} & {\tt 0000000000000000} & 1 \\
6     & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000004000000000} & 1 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0020000000000080} & 2 \\
      & {\tt 0000040000000010} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\ \hline

%Weight: 6
      & {\tt 0000000000100004} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0004400001000000} & {\tt 0000000000000000} & {\tt 0000000010000000} & {\tt 0000000000000000} & 4 \\
7     & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000004000000000} & 1 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0020000000000080} & 2 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000040000000010} & {\tt 0000000000000000} & 2 \\ \hline

%Weight: 10
      & {\tt 0000000000000000} & {\tt 0000000000100004} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0004400001000000} & {\tt 0000000000000000} & {\tt 0000000010000000} & {\tt 0000000000000000} & 4 \\
8     & {\tt 0400014000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000001000} & 4 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0020000000000080} & 2 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000040000000010} & {\tt 0000000000000000} & 2 \\ \hline

%Weight: 14
      & {\tt 0000000000000000} & {\tt 0000000000100004} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0000000010000000} & {\tt 0000000000000000} & {\tt 0004400001000000} & {\tt 0000000000000000} & 4 \\
9     & {\tt 0400014000000000} & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000001000} & 4 \\
      & {\tt 0220000080000080} & {\tt 0000000000000000} & {\tt 0000000800000000} & {\tt 1000000000004000} & 7 \\
      & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000040000000010} & {\tt 0000000000000000} & 2 \\ \hline

%Weight: 20
      & {\tt 0000000000000000} & {\tt 0000000000100004} & {\tt 0000000000000000} & {\tt 0000000000000000} & 2 \\
      & {\tt 0000000010000000} & {\tt 0000000000000000} & {\tt 0004400001000000} & {\tt 0000000000000000} & 4 \\
10    & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000001000} & {\tt 0400014000000000} & 4 \\
      & {\tt 0220000080000080} & {\tt 0000000000000000} & {\tt 0000000800000000} & {\tt 1000000000004000} & 7 \\
      & {\tt 4000140000000010} & {\tt 0000000000000000} & {\tt 0000400000000100} & {\tt 0000000000010000} & 7 \\ \hline

%Weight: 28
      & {\tt 0000100000100044} & {\tt 0000000200008000} & {\tt 0001000000000000} & {\tt 0000000008000200} & 9 \\
      & {\tt 0000000010000000} & {\tt 0000000000000000} & {\tt 0004400001000000} & {\tt 0000000000000000} & 4 \\
11    & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000001000} & {\tt 0400014000000000} & 4 \\
      & {\tt 0000000000000000} & {\tt 0000000800000000} & {\tt 1000000000004000} & {\tt 0220000080000080} & 7 \\
      & {\tt 4000140000000010} & {\tt 0000000000000000} & {\tt 0000400000000100} & {\tt 0000000000010000} & 7 \\ \hline

%Weight: 39
      & {\tt 0000100000100044} & {\tt 0000000200008000} & {\tt 0001000000000000} & {\tt 0000000008000200} & 9 \\
      & {\tt 0004500005000400} & {\tt 0000000000000000} & {\tt 0040000100000040} & {\tt 4000000000000000} & 10 \\
12    & {\tt 0000000000000000} & {\tt 0000000000000000} & {\tt 0000000000001000} & {\tt 0400014000000000} & 4 \\
      & {\tt 0000000000000000} & {\tt 0000000800000000} & {\tt 1000000000004000} & {\tt 0220000080000080} & 7 \\
      & {\tt 0000400000000100} & {\tt 0000000000010000} & {\tt 4000140000000010} & {\tt 0000000000000000} & 7 \\ \hline

%Weight: 53
      & {\tt 0000000008000200} & {\tt 0000100000100044} & {\tt 0000000200008000} & {\tt 0001000000000000} & 9 \\
      & {\tt 0004500005000400} & {\tt 0000000000000000} & {\tt 0040000100000040} & {\tt 4000000000000000} & 10 \\
13    & {\tt 0400114000040000} & {\tt 0020000000000080} & {\tt 0004000000400000} & {\tt 0000800100005002} & 14 \\
      & {\tt 0000000000000000} & {\tt 0000000800000000} & {\tt 1000000000004000} & {\tt 0220000080000080} & 7 \\
      & {\tt 0000400000000100} & {\tt 0000000000010000} & {\tt 4000140000000010} & {\tt 0000000000000000} & 7 \\ \hline

%Weight: 69
      & {\tt 0000000008000200} & {\tt 0000100000100044} & {\tt 0000000200008000} & {\tt 0001000000000000} & 9 \\
      & {\tt 0040000100000040} & {\tt 4000000000000000} & {\tt 0004500005000400} & {\tt 0000000000000000} & 10 \\
14    & {\tt 0400114000040000} & {\tt 0020000000000080} & {\tt 0004000000400000} & {\tt 0000800100005002} & 14 \\
      & {\tt 0228000280020080} & {\tt 0000040000000000} & {\tt 2000008000202008} & {\tt 1000004000004021} & 18 \\
      & {\tt 0000400000000100} & {\tt 0000000000010000} & {\tt 4000140000000010} & {\tt 0000000000000000} & 7 \\ \hline

%Weight: 69
      & {\tt 0000000008000200} & {\tt 0000100000100044} & {\tt 0000000200008000} & {\tt 0001000000000000} & 9 \\
      & {\tt 0040000100000040} & {\tt 4000000000000000} & {\tt 0004500005000400} & {\tt 0000000000000000} & 10 \\
15    & {\tt 0020000000000080} & {\tt 0004000000400000} & {\tt 0000800100005002} & {\tt 0400114000040000} & 14 \\
      & {\tt 0228000280020080} & {\tt 0000040000000000} & {\tt 2000008000202008} & {\tt 1000004000004021} & 18 \\
      & {\tt 0000400000000100} & {\tt 0000000000010000} & {\tt 4000140000000010} & {\tt 0000000000000000} & 7 \\ \hline

%Weight: 98
\end{tabular}
}
\end{center}
\end{table}
